### 2015-01-09 fundamentals/impl.tex
code review

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness \cite{citation_needed}. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
performance on and compatibility with resource computing infrastructures. This limitation severely 
increases the wall-clock time necessary to conduct parameterized sensitivity 
analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
which are flexible and support parallelization. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \gls{HTC} systems.

>>>>

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness when combined with code 
review \cite{cohen_modern_2010}. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. For example, if an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors, a variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

@@

Many fuel cycle simulators rely on \gls{COTS} and Windows-only software that limits 
performance on and compatibility with resource computing infrastructures. This limitation severely 
increases the wall-clock time necessary to conduct parameterized sensitivity 
analyses and other multi-simulation studies. \Cyclus, on the other hand, is 
primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms, 
which are flexible and support parallelization. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-only software. \Cyclus can therefore be easily deployed 
on large computer systems, such as \gls{HTC} systems.
